The \dealii Library, Version 9.5

### 2023-06-24 9.5/paper.tex
Update 9.5/paper.tex
Co-authored-by: Timo Heister <timo.heister@gmail.com>

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduce a free function that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation (in the form of \texttt{GridTools::Cache}) that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices.

@@

The above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()} internally to compute intersections between two geometric entities.

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.
\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template 
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // following parameter is optional would need additional
         // communication 
         consistent_numbering_of_sender_and_receiver);

>>>>

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduce a free function that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation (in the form of \texttt{GridTools::Cache}) that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices. The actual computation of the intersection of two geometric
entities is performed by the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}.

\todo[inline]{The following code snippet uses a different function
  that the text above. The connection between the two is not clear to me.}

@@

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.
\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template 
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // The following parameter is optional and setting it to 
         // true requires additional communication
         consistent_numbering_of_sender_and_receiver);
